---
title: "Kanye West"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---
```{r, include = FALSE}
library(spotifyr)
library(tidyverse)
library(usethis)
library(knitr)
library(compmus)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
About Kanye West Page
================

The Corpus: 
Most people know the hip-hop artist Kanye West.
One of the interesting things about him, was how his mental state 
affected what he was writing about, the feeling of the music and
how well it was recieved. I want to research through all the albums
of Kanye West, if there is actually a difference between the songs during the 
time he was manic, and later in his career when he calmed down. 

We will use eleven albums, nine of them are produced by Kanye West alone, and 
the other two are colabs. We will use the US sales to measure the success of 
each album. 
```{r}

```
Albums
================
Column 
-------------------------------------
    
### Chart 1
    
```{r}
```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r}
```   
 
### Chart 3
    
```{r}
```

```{r}

Kanye <- get_artist_audio_features("kanye west")
Kanye
by_album <- Kanye %>%
  filter(album_name == "The College Dropout" |
         album_name == "Late Registration" |
         album_name == "Graduation" | 
         album_name == "808s & Heartbreak" |
         album_name == "My Beautiful Dark Twisted Fantasy" |
         album_name == "Yeezus" |
         album_name == "The Life Of Pablo" |
         album_name == "ye" |
         album_name == "JESUS IS KING") %>%
  group_by(album_name, album_release_year) %>%
  summarize(valence = mean(valence),
            energy = mean(energy),
            tempo = mean(tempo))
  
ggplot(by_album, aes(x = album_release_year, y = valence, color = album_name)) +
    geom_point() +
    stat_smooth(method = "lm",
        col = "#C42126",
        se = FALSE,
        size = 1)

ggplot(by_album, aes(x = album_release_year, y = energy, color = album_name)) +
    geom_point() +
    stat_smooth(method = "lm",
        col = "#C42126",
        se = FALSE,
        size = 1)

ggplot(by_album, aes(x = album_release_year, y = tempo, color = album_name)) +
    geom_point() + 
    stat_smooth(method = "lm",
        col = "#C42126",
        se = FALSE,
        size = 1)
```

```{r cars}
summary(cars)
```

## R Markdown

The data:
Most people know the hip-hop artist Kanye West.
One of the interesting things about him, was how his mental state 
affected what he was writing about, the feeling of the music and
how well it was recieved. I want to research through all the albums
of Kanye West, if there is actually a difference between the songs during the 
time he was manic, and later in his career when he calmed down. 

```{r pressure, echo=FALSE}
plot(Kanye)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
